Seismic Time Series Analysis\\Statistics for Spatio-Temporal Data\\\textit{-- project draft --}

### 2020-06-08 project.after.Rmd
add mean/sd seasonplots

```{r seasonalities/seasonplot}
final.training.24 <- build_ts(final.training, periods = c(24))
seasonplot(final.training.24/sd(final.training.24, na.rm = T), type="l", col=rainbow(7))
legend("topleft", legend=weekdays(seis.train.start + (as.difftime(c(0:6), units="days"))), col=rainbow(7), lty=1, cex=0.8)

final.testing.24 <- build_ts(final.testing, periods = c(24))
seasonplot(final.testing.24/sd(final.testing.24, na.rm = T), type="l", col=rainbow(7))
legend("topleft", legend=weekdays(seis.test.final.start + (as.difftime(c(0:6), units="days"))), col=rainbow(7), lty=1, cex=0.8)

@@

plot_grid(
  autoplot(ts(seasonbase.after.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct daily"), size=1.5) +
    geom_line(aes(y=season.after.lockdown.24$figure, col="Multi daily")) +
    scale_colour_manual("", values=c("purple", "yellow"), breaks=c("Direct daily", "Multi daily")),
  autoplot(ts(seasonbase.after.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct weekly"), size=1.5) +
    geom_line(aes(y=season.after.lockdown.168$figure + rep(season.after.lockdown.24$figure, 7), col="Multi w+d")) +
    #geom_line(aes(y=rep(seasonbase.after.lockdown.24$figure, 7), col="Direct daily"), size=1.5) +
    #geom_line(aes(y=rep(season.after.lockdown.24$figure, 7), col="Multi daily")) +
    geom_line(aes(y=season.after.lockdown.168$figure, col="Multi weekly")) +
    scale_colour_manual("", values=c("red", "purple", "blue", "yellow", "green"), breaks=c("Direct weekly", "Direct daily", "Multi" %s+% c(" weekly", " daily", " w+d"))),
  nrow = 2)

@@

plot_grid(
  autoplot(ts(season.after.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = season.after.lockdown.24$figure - season.after.lockdown.24$sd, ymax = season.after.lockdown.24$figure + season.after.lockdown.24$sd), fill = "mediumpurple1", alpha=0.5) +
    geom_line(aes(col="Daily lockdown")) +
    geom_ribbon(aes(ymin = season.before.lockdown.24$figure - season.before.lockdown.24$sd, ymax = season.before.lockdown.24$figure + season.before.lockdown.24$sd), fill = "lightcoral", alpha=0.5) +
    geom_line(aes(y=season.before.lockdown.24$figure, col="Daily before")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("Daily lockdown", "Daily before")),
  autoplot(ts(season.after.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = season.after.lockdown.168$figure - season.after.lockdown.168$sd, ymax = season.after.lockdown.168$figure + season.after.lockdown.168$sd), fill = "mediumpurple1", alpha=0.5) +
    geom_line(aes(col="Weekly lockdown")) +
    geom_ribbon(aes(ymin = season.before.lockdown.168$figure - season.before.lockdown.168$sd, ymax = season.before.lockdown.168$figure + season.before.lockdown.168$sd), fill = "lightcoral", alpha=0.5) +
    geom_line(aes(y=season.before.lockdown.168$figure, col="Weekly before")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("Weekly lockdown", "Weekly before")),
nrow = 2)

autoplot(ts(seasonbase.after.lockdown.168$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
  geom_ribbon(aes(ymin = seasonbase.after.lockdown.168$figure - seasonbase.after.lockdown.168$sd, ymax = seasonbase.after.lockdown.168$figure + seasonbase.after.lockdown.168$sd), fill = "mediumpurple1", alpha=0.5) +
  geom_line(aes(col="Weekly lockdown")) +
  geom_ribbon(aes(ymin = seasonbase.before.lockdown.168$figure - seasonbase.before.lockdown.168$sd, ymax = seasonbase.before.lockdown.168$figure + seasonbase.before.lockdown.168$sd), fill = "lightcoral", alpha=0.5) +
  geom_line(aes(y=seasonbase.before.lockdown.168$figure, col="Weekly before")) +
  scale_colour_manual("", values=c("purple", "red"), breaks=c("Weekly lockdown", "Weekly before"))
```

>>>>

```{r seasonalities/seasonplot}
before.lockdown.start <- seis.train.start
before.lockdown.end <- as_datetime('2020-03-14T00:00:00') - seconds(1)
after.lockdown.start <- as_datetime('2020-03-14T00:00:00')
after.lockdown.end <- as_datetime('2020-04-26T00:00:00') - seconds(1)
before.lockdown <- build_ts(seis.h, periods = c(24), start = before.lockdown.start, end = before.lockdown.end, force_ms = T)
after.lockdown <- build_ts(seis.h, periods = c(24), start = after.lockdown.start, end = after.lockdown.end, force_ms = T)
# We first check the seasonplots, highlighting different weekdays. We divide by sd to account for spikes
seasonplot(before.lockdown/sd(before.lockdown, na.rm=T), type="l", col=rainbow(7), main="Seasonal plot: before lockdown")
legend("topleft", legend=weekdays(before.lockdown.start + (as.difftime(c(0:6), units="days"))), col=rainbow(7), lty=1, cex=0.8)
seasonplot(after.lockdown/sd(after.lockdown, na.rm=T), type="l", col=rainbow(7)[c(6:7,1:5)], main="Seasonal plot: after lockdown")
legend("topleft", legend=weekdays(after.lockdown.start + (as.difftime(c(0:6), units="days")))[c(3:7,1:2)], col=rainbow(7), lty=1, cex=0.8)

@@

plot_grid(
  autoplot(ts(seasonbase.after.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct daily"), size=1.5) +
    geom_line(aes(y=season.after.lockdown.24$figure, col="Multi daily")) +
    scale_colour_manual("", values=c("purple", "yellow"), breaks=c("Direct daily", "Multi daily")),
  autoplot(ts(seasonbase.after.lockdown.168$figure[c(49:168,1:48)], frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() + geom_line(aes(col="Direct weekly"), size=1.5) +
    geom_line(aes(y=season.after.lockdown.168$figure[c(49:168,1:48)] + rep(season.after.lockdown.24$figure, 7), col="Multi w+d")) +
    #geom_line(aes(y=rep(seasonbase.after.lockdown.24$figure, 7), col="Direct daily"), size=1.5) +
    #geom_line(aes(y=rep(season.after.lockdown.24$figure, 7), col="Multi daily")) +
    geom_line(aes(y=season.after.lockdown.168$figure[c(49:168,1:48)], col="Multi weekly")) +
    scale_colour_manual("", values=c("red", "purple", "blue", "yellow", "green"), breaks=c("Direct weekly", "Direct daily", "Multi" %s+% c(" weekly", " daily", " w+d"))),
  nrow = 2)

@@

plot_grid(
  autoplot(ts(season.after.lockdown.24$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = season.after.lockdown.24$figure - season.after.lockdown.24$sd, ymax = season.after.lockdown.24$figure + season.after.lockdown.24$sd), fill = "mediumpurple1", alpha=0.5) +
    geom_line(aes(col="Daily lockdown")) +
    geom_ribbon(aes(ymin = season.before.lockdown.24$figure - season.before.lockdown.24$sd, ymax = season.before.lockdown.24$figure + season.before.lockdown.24$sd), fill = "lightcoral", alpha=0.5) +
    geom_line(aes(y=season.before.lockdown.24$figure, col="Daily before")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("Daily lockdown", "Daily before")),
  autoplot(ts(season.after.lockdown.168$figure[c(49:168,1:48)], frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
    geom_ribbon(aes(ymin = (season.after.lockdown.168$figure - season.after.lockdown.168$sd)[c(49:168,1:48)], ymax = (season.after.lockdown.168$figure + season.after.lockdown.168$sd)[c(49:168,1:48)]), fill = "mediumpurple1", alpha=0.5) +
    geom_line(aes(col="Weekly lockdown")) +
    geom_ribbon(aes(ymin = season.before.lockdown.168$figure - season.before.lockdown.168$sd, ymax = season.before.lockdown.168$figure + season.before.lockdown.168$sd), fill = "lightcoral", alpha=0.5) +
    geom_line(aes(y=season.before.lockdown.168$figure, col="Weekly before")) +
    scale_colour_manual("", values=c("purple", "red"), breaks=c("Weekly lockdown", "Weekly before")),
nrow = 2)

autoplot(ts(seasonbase.after.lockdown.168$figure[c(49:168,1:48)], frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
  geom_ribbon(aes(ymin = (seasonbase.after.lockdown.168$figure - seasonbase.after.lockdown.168$sd)[c(49:168,1:48)], ymax = (seasonbase.after.lockdown.168$figure + seasonbase.after.lockdown.168$sd)[c(49:168,1:48)]), fill = "mediumpurple1", alpha=0.5) +
  geom_line(aes(col="Weekly lockdown")) +
  geom_ribbon(aes(ymin = seasonbase.before.lockdown.168$figure - seasonbase.before.lockdown.168$sd, ymax = seasonbase.before.lockdown.168$figure + seasonbase.before.lockdown.168$sd), fill = "lightcoral", alpha=0.5) +
  geom_line(aes(y=seasonbase.before.lockdown.168$figure, col="Weekly before")) +
  scale_colour_manual("", values=c("purple", "red"), breaks=c("Weekly lockdown", "Weekly before"))
```
```{r seasonalities/seasonplot-mean-sd}
weekdays <- c("Monday", "Tuesday", "Wednseday", "Thursday", "Friday", "Saturday", "Sunday")

seasonbase.before.lockdown.168.df <- data.frame(hour=rep(1:24, 7), mean=seasonbase.before.lockdown.168$figure[1:168], sd=seasonbase.before.lockdown.168$sd[1:168], Weekday=rep(weekdays, each=24))
ggplot(data=seasonbase.before.lockdown.168.df) +
  geom_line(aes(hour, mean - sd, col=Weekday), alpha=.1) +
  geom_line(aes(hour, mean + sd, col=Weekday), alpha=.1) +
  geom_ribbon(aes(hour, ymin = mean - sd, ymax = mean + sd, fill = Weekday), alpha=0.1, show.legend=F) +
  geom_line(aes(hour, mean, col=Weekday)) +
  ylab("Mean hourly movement (nm)") +
  scale_color_manual(values = rainbow(7), breaks=weekdays, aesthetics = c("colour", "fill"))

seasonbase.after.lockdown.168.df <- data.frame(hour=rep(1:24, 7), mean=seasonbase.after.lockdown.168$figure[c(49:168,1:48)], sd=seasonbase.after.lockdown.168$sd[c(49:168,1:48)], Weekday=rep(weekdays, each=24))
ggplot(data=seasonbase.after.lockdown.168.df) +
  geom_line(aes(hour, mean - sd, col=Weekday), alpha=.1) +
  geom_line(aes(hour, mean + sd, col=Weekday), alpha=.1) +
  geom_ribbon(aes(hour, ymin = mean - sd, ymax = mean + sd, fill = Weekday), alpha=0.1, show.legend=F) +
  geom_line(aes(hour, mean, col=Weekday)) +
  ylab("Mean hourly movement (nm)") +
  scale_color_manual(values = rainbow(7), breaks=weekdays, aesthetics = c("colour", "fill"))
```
